Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
Add the word "modern" here, and a footnote.

Type dispatching is the process of finding the concrete implementation that is
applicable to the objects at hand when doing a generic operation on them. An
example would be the addition of two objects: The addition needs to check what
the concrete objects that should be added are, and choose the implementation
that is fitting for them. Type dispatching is a very common operation in a
dynamic language because no types are known at compile time, so all operations
need it.

>>>>

Type dispatching is the process of finding the concrete implementation that is
applicable to the objects at hand when doing a generic operation on them. An
example would be the addition of two objects: The addition needs to check what
the concrete objects that should be added are, and choose the implementation
that is fitting for them. Type dispatching is a very common operation in
modern\footnote{For languages in the LISP family, basic arithmetic operations
are typically not overloaded; even in Smalltalk, type dispatching is much
simpler than in Python or JavaScript.}
dynamic languages because no types are known at compile time, so all operations
need it.
